Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-08-20 workflow/workflow.Rmd
Update workflow.Rmd
Sandrine: Minor edits to text and figure captions.

One drawback of this strategy is that the logarithm is not a variance stabilizing transformation. Variance stabilizing transformations based on the negative binomial distribution are available, e.g., in the `DESeq2` package, and may be a better choice in real data analyses. Note that the `makeFilterStats` function of `clusterExperiment` can be used with any user-supplied function. Here, we show an example with the `vst` function from `DESeq2`.

@@

```{r bic, fig.cap="BIC of the model with different values of K."}
k_values <- c(1: 5, 10)
plot(k_values, sapply(fit, zinbBIC, t(counts(dataObj))), 
     ylab = "BIC", xlab = "K", type = "b")
```

```{r aic, fig.cap="AIC of the model with different values of K."}
plot(k_values, sapply(fit, zinbAIC, t(counts(dataObj))),
     ylab = "AIC", xlab = "K", type = "b")
```

@@

```{r examinemakeConsensus, fig.cap="RSEC: Candidate clusterings found using the function RSEC from the clusterExperiment package. The top row corresponds to the consensus clustering and is color-coded accordingly. The other rows correspond to the individual clustering across which the consensus was computed. In each row, the color is chosen to match as close as possible the color of the cluster from the previous row with the largest overlap."}
plotClusters(dataObj, existingColors = "firstOnly")
```

>>>>

One drawback of this strategy is that the logarithm is not a variance-stabilizing transformation. Variance-stabilizing transformations based on the negative binomial distribution are available, e.g., in the `DESeq2` package, and may be a better choice in real data analyses. Note that the `makeFilterStats` function of `clusterExperiment` can be used with any user-supplied function. Here, we show an example with the `vst` function from `DESeq2`.

@@

```{r bic, fig.cap="ZINB-WaVE: BIC of model for different values of K."}
k_values <- c(1: 5, 10)
plot(k_values, sapply(fit, zinbBIC, t(counts(dataObj))), 
     ylab = "BIC", xlab = "K", type = "b")
```

```{r aic, fig.cap="ZINB-WaVE: AIC of model for different values of K."}
plot(k_values, sapply(fit, zinbAIC, t(counts(dataObj))),
     ylab = "AIC", xlab = "K", type = "b")
```

@@

```{r examinemakeConsensus, fig.cap="RSEC: Candidate clusterings found using the function RSEC from the clusterExperiment package. The top row corresponds to the consensus clustering and is color-coded accordingly. The other rows correspond to the individual clusterings across which the consensus was computed. In each row, the colors are chosen to match as closely as possible with the colors of clusters with the largest overlap from the previous row."}
plotClusters(dataObj, existingColors = "firstOnly")
```
